The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-12-23 manuscript.Rmd
add more context to diversity fractions

This underrepresentation is also manifest in the intensity of the collecting effort. In OBIS records for the US EEZ, marine invertebrates represent `r invert_props$prop_obis_invert_samples`% of the occurrences but `r invert_props$prop_obis_invert_species`% of the total number of species; and in iDigBio, they represent `r invert_props$prop_idigbio_invert_samples`% of the records but `r invert_props$prop_idigbio_invert_species`% of the species. In contrast, marine vertebrates represent `r invert_props$prop_idigbio_vert_samples`% of the samples and `r invert_props$prop_idigbio_vert_species`% of the species in iDigBio, and `r invert_props$prop_obis_vert_samples`% of the samples and `r invert_props$prop_obis_vert_species`% of the species in OBIS (Fig. \@ref(fig:kingdom-diversity-plot)). In other words, while marine invertebrates are represented at a level on par with their diversity in the marine fraction of the databases, each species is represented by fewer samples compared to vertebrates (median number of records per species for invertebrates `r median_idigbio_invert` and `r median_obis_invert`, _vs_ and `r median_idigbio_vert` and `r median_obis_vert` for vertebrates, for iDigBio and OBIS respectively).

>>>>

This underrepresentation is also manifest in the intensity of the collecting effort. Marine invertebrates are estimated to represent  `r total_invert_prop`% of the global marine diversity[@worms-stats]. In OBIS records for the US EEZ, marine invertebrates represent `r invert_props$prop_obis_invert_samples`% of the occurrences but `r invert_props$prop_obis_invert_species`% of the total number of species; and in iDigBio, they represent `r invert_props$prop_idigbio_invert_samples`% of the records but `r invert_props$prop_idigbio_invert_species`% of the species. In contrast, marine vertebrates represent `r invert_props$prop_idigbio_vert_samples`% of the samples and `r invert_props$prop_idigbio_vert_species`% of the species in iDigBio, and `r invert_props$prop_obis_vert_samples`% of the samples and `r invert_props$prop_obis_vert_species`% of the species in OBIS (Fig. \@ref(fig:kingdom-diversity-plot)). In other words, while marine invertebrates are represented at a level on par with their diversity within the US EEZ in the databases, each species is represented by fewer samples than for vertebrates (median number of records per species for invertebrates `r median_idigbio_invert` and `r median_obis_invert`, _vs_ and `r median_idigbio_vert` and `r median_obis_vert` for vertebrates, for iDigBio and OBIS respectively).
